\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.0cm, top=0.8cm, right=0.9cm, bottom=0.6cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning
\renewcommand{\baselinestretch}{0.95} % Reduce line spacing globally

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.1mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.5mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.1mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.5mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=0.5mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.1mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{ABHINAV KUMAR}} \\
    \vspace{2mm}
    \small{
    \socialicon{\faPhone} {+91-7500024959}
 | \socialicon{\faEnvelope} \href{mailto:abhikumar3584@gmail.com}{abhikumar3584@gmail.com}
    } \\
    \vspace{1.5mm}
    \small{
    % \socialicon{\faUniversity} \href{mailto:152103@cic.du.ac.in}{152103@cic.du.ac.in} |
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/abhinav-kumar-0ba731239/}{Linked-in} | 
    \socialicon{\faGithub} \href{https://github.com/Abhinavkumar3584}{Github} | 
    \socialicon{\faTwitter} \href{https://x.com/ABHINAV11555548}{Twitter}
    | \socialicon{\faUser} \href{https://portfolioabhinavkumar.vercel.app/}{Portfolio}
    }
\end{center}

\vspace{2mm}

\section{\textbf{Interest}}
\small{
Frontend Development, Data Analysis and Visualization, Research and Development, Graphic Design and UI/UX, Artificial Intelligence and Machine Learning, Innovation and Entrepreneurship, and Prompt Engineering.
}

\section{\textbf{Experience}}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Pratiyogita Setu [\href{https://psetu.com/}{\faIcon{globe}}]}{India}
    {Founder}{Feb 2025 - Present}
    \resumeItemListStart
      \item Launched an AI-powered exam prep platform for competitive exam aspirants.
      \item Developed \textbf{Pariksha Yogya}, an eligibility and attempt tracker to help students understand their exam qualifications.
      \item Designed \textbf{Pariksha Marg}, a structured syllabus roadmap for systematic and effective learning.
      \item Built \textbf{Pariksha Gyan}, an AI chatbot that provides real-time explanations, topic-wise PYQs, and Q\&A insights.

     
    \resumeItemListEnd

  \resumeSubheading
    {CHEGG [\href{https://www.chegg.com/}{\faIcon{globe}}]}{Remote}
    {Subject Matter Expert}{Sept 2023 - Present}
    \resumeItemListStart
      \item Solved complex problems related to Data Structures and Algorithms, Computer Networking, and Programming.
      \item Successfully addressed \textbf{100+} questions, provided detailed explanations and solutions, maintaining \textbf{95} accuracy.
    \resumeItemListEnd

  \resumeSubheading
    {Gloomweb Solutions [\href{https://gloomweb.com}{\faIcon{globe}}]}{Remote (Client: Canada)}
    {Frontend Developer Intern}{Apr 2025 – Jun 2025}
    \resumeItemListStart
     \item Translated Figma designs into responsive and accessible web UI using HTML, CSS, Tailwind CSS, and JavaScript.
     \item Collaborated team in an Agile product development environment to deliver scalable and production-ready front-ends, maintain clean, well-documented code, and ensure seamless back-end integration.

    \resumeItemListEnd

    \resumeSubheading
    {Big and Best Mart}{India}
    {Frontend Developer}{Dec 2024 - Feb 2025}
    \resumeItemListStart
      \item Developed an e-commerce platform for selling stationery and daily essentials.
      \item Designed and implemented a user-friendly interface for seamless online shopping.
      \item Focused on optimizing website performance and ensuring a smooth customer experience.
    \resumeItemListEnd

  \resumeSubheading
    {CLUSTER INNOVATION CENTRE, UNIVERSITY OF DELHI [\href{https://cic.du.ac.in/}{\faIcon{globe}}]}{Delhi, India}
    {AI and ML, Chatbot Development}{July 2024 - Nov 2024}
    \resumeItemListStart
      \item Developed an AI chatbot using NLP models (Google-BERT, Sentence Transformers) and Pinecone for vector database to deliver precise answers from NCERT content for competitive exam (UPSC, SSC, etc).
      \item Built Django Web App enabling users to query questions and receive accurate responses efficiently.
      \item Optimized data pre-processing and query matching algorithms to enhance retrieval speed and accuracy.
    \resumeItemListEnd

  \resumeSubheading  
    {Sewa International [\href{https://sewausa.org}{\faIcon{globe}}]}{Hybrid, India}  
    {Website \& Digital Outreach Volunteer}{May 2024 – Jul 2024}  
    \resumeItemListStart  
      \item Managed and maintained website on Wild Apricot, Update pages aligned with upcoming events and Programs.    
      \item Improved website SEO health score from \textbf{45 to 75}.  
      \item Engaged in Grassroots Leadership Camp, co-organized SEWA FELLOWSHIP, and guided \textbf{120+} candidates.
    \resumeItemListEnd

    \resumeSubheading
      {{BEYONDEXAMS [\href{https://beyondexams.org/}{\faIcon{globe}}]}}{Delhi, India}
      {AI Youtube video Classifier}{July 2022 - Nov 2022}
      \resumeItemListStart
        \item Built an AI model using Python and Scikit-learn to classify YouTube videos as educational or non-educational.
        \item Developed a user-friendly website and initiated a Chrome extension for seamless video classification.
      \resumeItemListEnd 
      
  \resumeSubHeadingListEnd

\section{\textbf{Education}}
\resumeSubHeadingListStart

\resumeSubheading
{Cluster Innovation centre, University of delhi}{Delhi, India}
{B.tech (Information Technology and Mathematical Innovation)}{Nov 2021 - June 2025}
\resumeItemListStart
\item CGPA: 8.24/10
\resumeItemListEnd

\resumeSubheading
{Maa Bhargwati International School}{Bulandshahr, India}
{Intermediate}{March 2021}

\resumeSubheading
{Rashtriya Military School , Ajmer }{Ajmer, India}
{Secondary Education}{March 2019}

\resumeSubHeadingListEnd

\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeProject
  {Need DU: Web platform for Delhi University students}
  {Tools: HTML, CSS, JavaScript, SQL, React}
  {}
  {{}[\href{https://github.com/Abhinavkumar3584/Need-DU}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Created a web platform enabling Delhi University students to connect.
  \item Integrated features to access College exam PYQ, buy/sell items, and find nearby accommodations to their colleges.
 
\resumeItemListEnd

\resumeProject
  {Analysis of Agritech Startups in India}
  {Tools: Data analysis tools (e.g., Python, Excel)}
  {}
  {{}}
\resumeItemListStart
  \item Conducted in-depth analysis of Agritech startups, identifying growth trends and challenges - urban and rural.
  \item Examined the advantages of technology integration in the agricultural sector, Prons and cons.
  
\resumeItemListEnd

\resumeProject
  {Cloud Resource Manager Software}
  {Tools: React.js, Node.js}
  {}
  {{}}
\resumeItemListStart
  \item  Engineered a monitoring system for personal servers, with a Django backend for system resource data
collection.
  \item Designed Figma screens and frontend created with React.js for real-time data visualization and user interaction and Integrated Node.js for user authentication and MongoDB for storage.
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Skills}}
\resumeItemListStart
 
  \resumeItem{Programming Languages:}
    {Python, C/C++, Java, HTML, CSS, Javascript}
  \resumeItem{Developer Tools} % Category
    {Visual Studio Code, Git, GitHub}
  \resumeItem{Frameworks \& Libraries}
    {React.js, Django, OpenCV, Scikit-learn} 
  \resumeItem{Cloud \& Databases}
    {SQL, Pinecone}
  \resumeItem{Operating Systems}
    {Windows, Linux}
  \resumeItem{Graphics \& UI/UX designing tools:}
    {Canva, Figma}
  \resumeItem{AI \& Automation Tools:}
    {Github Copilot, Lovable.dev, Bolt.dev, ChatGPT, Gemini}
  \resumeItem{CMS \& Web Tools:}
    {WordPress, Zoho, Wild Apricot, SEO}
  
  
\resumeItemListEnd

\section{\textbf{Achievements and Position of Responsibility}}
\resumeItemListStart
 
  \resumeItem{}
    {Cleared All India Rashtriya Military School Entrance Exam and Sainik School Entrance Exam.}
  \resumeItem{}
    {Selected for B.Tech (Information Technology and Mathematical Innovation) at Cluster Innovation Centre, University of Delhi, among 50 seats.} 
  \resumeItem{}
    {Secured fourth position in hackathon organized by Beyond Exams.}
  \resumeItem{}
    {Core team member of college hackathon (Convoke 5.0) organizing team, managing logistics and event planning.}
 
\resumeItemListEnd
 
\section{\textbf{Certifications}}
\resumeItemListStart
    \item \textbf{Sewa International:} Grassroot Leadership Camp Volunteer (Jaipur) \hfill \textit{21 June - 22 June, 2025}[\href{https://indiancc.nic.in/}{\faIcon{globe}}]
    \item \textbf{National Cadet Corps:} Combined Annual Training Camp - (2023, 2024) \hfill \textit{15 - 24 July, 2024}[\href{https://indiancc.nic.in/}{\faIcon{globe}}]
    \item \textbf{National Cadet Corps:} All India UP Trekking Camp \hfill \textit{10 Nov - 17 Nov, 2024}[\href{https://indiancc.nic.in/}{\faIcon{globe}}]
    \item \textbf{Beyond Exams:} Hack2Educate Hackathon Participant \hfill \textit{11 Nov - 13 Nov, 2022}[\href{https://indiancc.nic.in/}{\faIcon{globe}}]
    \item \textbf{IIRS E-Learning:} Geographic Information System Overview \hfill \textit{3 Oct - 27 Oct, 2022}[\href{https://indiancc.nic.in/}{\faIcon{globe}}]
    

\resumeItemListEnd

% Extra-Curricular Activities Section
\section{\textbf{Extra-Curricular Activities}}
\resumeSubHeadingListStart
  \resumeSubheading
      {{National Cadet Corps }}{Delhi, India}
      {Rank:CADET}{Nov 2022 - April 2025}
     \resumeItemListStart
        \item Completed Combined Annual Training Camp,2022 and 2023 , leading and managing a team of \textbf{50+} cadets.
        \item Completed All India UP Trekking Camp with rank Company 2IC, commanding a team of 101 cadets.
        \item Successfully passed National Cadet Corps \textbf{Certificate - B} with \textbf{"B"} grade and \textbf{Certificate - C} with \textbf{"A"} grade.
        
      \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}